---
title: "Time Series Project"
author: "Bo Yun"
date: "3/24/2021"
output: html_document
---

# Introduction
```{r}
# This data is Website traffic, which can be important for many reasons. The more people see your site, the more potential customers you will have. The number of visitors to your website becomes the number of opportunities your business has at giving an impression, generating qualified leads, sharing your brand and building relationships.


# data source: https://www.kaggle.com/bobnau/daily-website-visitors
```

# Data import and clean
```{r}
library(dplyr)
library(tswge)
library(ggplot2)
library(GGally)
library(tseries)

df=read.csv("~/Desktop/SMU/DS 6373 Time Series/Project/daily-website-visitors.csv")

df=df[1:500,] #Trim down the data
df
dim(df) #2167 entries and 5 variables, Page.Loads is the response variable. 


#--------------- Data cleaning - checking NA and data type---------------
sum(is.na(df$col)) # No NA values

#--------------- Data overview---------------
plotts.sample.wge(df$Page.Loads) 
mean(df$Page.Loads)
```

# Stationarity Check
```{r}
#--------------- Visual check ---------------
plotts.sample.wge(df$Page.Loads) 
aic5.wge(df$Page.Loads) #ARMA(5,2) for the target variable

#--------------- Augmented Dickey-Fuller test ---------------
adf.test(df$Page.Loads) # p-value smaller than 0.05 => Stationary 


#--------------- Condition 1 - Constant mean ---------------
mean(df$Page.Loads)
# Appears to have constant mean
# Seasonality is breaking the condition 1 of constant mean. 
# Domain knowledge - it's a daily record so a weekly trend is expected (s=7)


#---------------Condition 2 - Constant variance ---------------
# Appears to have constant variance 


#--------------- Condition 3 - Constant correlation ---------------
# Compare acf of first half and second half 
df1=df[1:150,]
df1
df2=df[151:300,]
df2
acf(df1$Page.Loads) 
acf(df2$Page.Loads)    # Compared => Constant correlation

############# Conclusion ############
# The data is non-stationary 
```
===============================================================================================================
#============================================ Univariate Model ================================================
===============================================================================================================
# Model 1 - ARMA model (Univariate model)
```{r}
#--------------- Finding the best model based on AIC and BIC ---------------
plotts.sample.wge(df$Page.Loads) 
aic5.wge(df$Page.Loads) #ARMA(5,2) for both AIC and BIC
aic5.wge(df$Page.Loads, type='bic')
acf(df$Page.Loads)
pacf(df$Page.Loads)


#--------------- Checking cross correlation between variables to see lag efffect ---------------
ccf(df$Page.Loads,df$Unique.Visits)  # no lag
ccf(df$Page.Loads,df$First.Time.Visits) # no lag
ccf(df$Page.Loads,df$Returning.Visits) # no lag


fit=est.arma.wge(df$Page.Loads,p=5,q=2)
fit  

mean(df$Page.Loads)

#phi=1.7891, -2.0469 ,1.7728 ,-1.3226, 0.7625
#theta=1.0121871, -0.7784402
#mean=3954.95
#variance=174725.7
#aic=12.12

#------------- factoring the phi and theta for the equation write up --------------
factor.wge(phi=c(1.7891, -2.0469 ,1.7728 ,-1.3226, 0.7625))
factor.wge(phi=c(1.0121871, -0.7784402))


#--------------- Final ARMA model - factored form ---------------
# (1-0.9729B)(1-1.2426B+0.9954B^2)(1+0.4264B+0.7873B^2)(Xt-3954.95)=(1-1.0122B+0.7784B^2)at, variance=181171.8


#-----------------Validating the model - Last 10 data points - ASE ------------
f=fore.arma.wge(df$Page,phi=c(1.7891, -2.0469 ,1.7728 ,-1.3226, 0.7625),theta=c(1.0121871, -0.7784402), n.ahead=20,limits=F, lastn=T, plot=T)
plot(as.numeric(df$Page.Loads), type = "l", xlim = c(200,520),ylab = "Daily Website Visit", main = "20 Day Website Visit Forecast ")
lines(seq(481,500,1),f[[1]], col = "red")

# ASE
ASE=mean((f$f-df$Page.Loads[481:500])^2)
ASE


#--------------- Validating the model - Rolling ASE -----------------
# Model 
phis = c(1.7891, -2.0469 ,1.7728 ,-1.3226, 0.7625 )
thetas = c(1.0121871, -0.7784402)
s  = 0
d  = 0


trainingSize = 100
test = 10
ASEHolder = numeric()

for( i in 1:(500-(trainingSize + test) + 1))
{
  forecasts = fore.arma.wge(df$Page.Loads[i:(i+(trainingSize-1))],phi = phis, theta = thetas,n.ahead = test)
  
  ASE = mean((df$Page.Loads[(trainingSize+i):(trainingSize+ i + (test) - 1)] - forecasts$f)^2)
  
  ASEHolder[i] = ASE
  if(i == 105) 
  {print(forecasts$f)}
}
ASEHolder<-ASEHolder[!is.na(ASEHolder)]
ASEHolder
hist(ASEHolder)

WindowedASE = mean(ASEHolder)
summary(ASEHolder)
WindowedASE

# Visualization
i = 100
fs = fore.arma.wge(df$Page.Loads[i:(i+(trainingSize+test)-1)],phi = phis, theta = thetas,n.ahead = 10, lastn = TRUE, limit=FALSE)
ASE = mean((df$Page.Loads[(i+trainingSize):(i+(trainingSize+test)-1)] - fs$f )^2)
ASE



#------------------------------ Short term prediction - 20 points ahead ------------------------------
f=fore.arma.wge(df$Page,phi=c(1.7891, -2.0469 ,1.7728 ,-1.3226, 0.7625),theta=c(1.0121871, -0.7784402), n.ahead=20,limits=T, lastn=F, plot=T)
plot(as.numeric(df$Page), type = "l", xlim = c(1,510))
lines(seq(500,519,1),f[[1]], col = "red")


#------------------------------ Long term prediction - 200 points ahead ------------------------------
f=fore.arma.wge(df$Page,phi=c(1.7891, -2.0469 ,1.7728 ,-1.3226, 0.7625),theta=c(1.0121871, -0.7784402), n.ahead=200,limits=T, lastn=F, plot=T)
plot(as.numeric(df$Page), type = "l", xlim = c(1,710))
lines(seq(500,699,1),f[[1]], col = "red")

```


#=============================== Model 2 - ARIMA(3,1,1) with s=7 - (Univariate model) ===============================
```{r}
#--------------- Taking out (1-B) unit roots term ---------------


# Identify non-stationarities using Tiao/Tsay overfitting table, i-> Both high AR models show (1-B) term once
est.ar.wge(df$Page.Loads, p=6, type='burg')
est.ar.wge(df$Page.Loads, p=8, type='burg')

plotts.sample.wge(df$Page.Loads) 


#--------------- Identify seasonality using overfitting---------------
factor.wge(phi=c(rep(0,6),1)) # It appears that the period is 7 from realization and acf plot. Compare this with an overfitting AR model 
est.ar.wge(df$Page.Loads, p=14, type='burg')


#--------------- Differencing the original data with (1-B) and (1-B^7)---------------
y=artrans.wge(df$Page.Loads,phi.tr=1)
y=artrans.wge(y,phi.tr=c(rep(0,6),1))

acf(y) # Visually looks white noise 
ljung.wge(y) # Ljung box method doesn't quite qualify it as a white noise. 

#--------------- Finding ARMA model for the difference data---------------
aic5.wge(y) #ARMA(3,1) 
aic5.wge(y,type='bic')
fit=est.arma.wge(y,p=3,q=1)
mean(df$Page.Loads)

?fore.aruma.wge

#----------------- Final ARIMA model - factored form -----------------
# (1-B)(1-0.8404B)(1-0.0107B+0.1290B^2)(1-B^7)(Xt-3954.95)=(1-B)at, variance=141342.4

factor.wge(phi=c(1.7891, -2.0469 ,1.7728 ,-1.3226, 0.7625))

#----------------- Validating the model - Last 20 data points - ASE -----------------
f=fore.aruma.wge(df$Page.Loads,phi=c(0.8511057 ,-0.1379100 , 0.1083783),theta=c(0.999999995),d=1,s=7,n.ahead=20,limits=F, lastn=T, plot=T)

plot(as.numeric(df$Page.Loads), type = "l", xlim = c(1,520),ylab = "Daily Website Visit", main = "20 Day Website Visit Forecast ")
lines(seq(481,500,1),f[[1]], col = "red")

# ASE
ASE=mean((f$f-df$Page.Loads[481:500])^2)
ASE


#----------------- Validating the model - Rolling ASE -----------------
# Model 
phis = c(0.8511057 ,-0.1379100 , 0.1083783)
thetas = c(1)
s  = 7
d  = 1


trainingSize = 100
test = 10
ASEHolder = numeric()

for( i in 1:(500-(trainingSize + test) + 1))
{
  forecasts = fore.arma.wge(df$Page.Loads[i:(i+(trainingSize-1))],phi = phis, theta = thetas,n.ahead = test)
  
  ASE = mean((df$Page.Loads[(trainingSize+i):(trainingSize+ i + (test) - 1)] - forecasts$f)^2)
  
  ASEHolder[i] = ASE
  if(i == 105) 
  {print(forecasts$f)}
}
ASEHolder<-ASEHolder[!is.na(ASEHolder)]
ASEHolder
hist(ASEHolder)

WindowedASE = mean(ASEHolder)
summary(ASEHolder)
WindowedASE

# Visualization
i = 80
fs = fore.aruma.wge(df$Page.Loads[i:(i+(trainingSize+test)-1)],phi = phis, theta = thetas,s=7, d=1,n.ahead = 10, lastn = TRUE, limit=FALSE)
ASE = mean((df$Page.Loads[(i+trainingSize):(i+(trainingSize+test)-1)] - fs$f )^2)
ASE


#--------------- Short term prediction - 20 points ahead ---------------
f=fore.aruma.wge(df$Page,phi=c(0.8511057 ,-0.1379100 , 0.1083783),theta=c(0.999999995),d=1,s=7,n.ahead=20,limits=T, lastn=F, plot=T)
plot(as.numeric(df$Page), type = "l", xlim = c(1,520))
lines(seq(500,519,1),f[[1]], col = "red")


#---------------Long term prediction - 200 points ahead ---------------
f=fore.aruma.wge(df$Page,phi=c(0.8511057 ,-0.1379100 , 0.1083783),theta=c(0.999999995),d=1,s=7,n.ahead=200,limits=T, lastn=F, plot=T)
plot(as.numeric(df$Page), type = "l", xlim = c(1,710),ylim=c(1,20000))
lines(seq(500,699,1),f[[1]], col = "red")

```


#=============================== Model 3 - ARIMA(3,0,2) with s=7 - (Univariate model) ==========================
```{r}

# Identify seasonality using overfitting (7 days)

factor.wge(phi=c(rep(0,6),1)) # It appears that the period is 7 from realization and acf plot. Compare this with an overfitting AR model 
est.ar.wge(df$Page.Loads, p=14, type='burg')


#--------------- Differencing the original data with (1-B^365) and (1-B^7)---------------
y=artrans.wge(y,phi.tr=c(rep(0,6),1))

acf(y) # Visually looks white noise 
ljung.wge(y,K=24)
ljung.wge(y,K=48) # Ljung box method doesn't quite qualify it as a white noise. 

# Finding ARMA model for the difference data
aic5.wge(y) #ARMA(3,2) 
fit=est.arma.wge(y,p=3,q=2)
mean(df$Page.Loads)



factor.wge(phi=c(-0.005399671 ,-0.654709018,  0.158526224))
factor.wge(phi=c(-0.4246388 ,-0.9999976))

#-------------------Final ARIMA model - factored form ------------------
# (1-B^7)(1-0.2244B)(1+0.2298B+0.7063B^2)(Xt-3954.95)=(1+0.4246B+1.0000B^2)at, variance=141342.4

# factor.wge(phi=c(1.1734189 ,-1.3154322,  0.4784634))  #for phi
# factor.wge(phi=c(0.7709449, -1))  # for theta


#--------------- Validating the model - Last 20 data points - ASE -----------------

f=fore.aruma.wge(df$Page,phi=c(-0.005399671 ,-0.654709018,  0.158526224),theta=c(-0.4246388 ,-0.9999976),s=7,n.ahead=20,limits=F, lastn=T, plot=T)

plot(as.numeric(df$Page.Loads), type = "l", xlim = c(1,520),ylim=c(0,7000), ylab = "Daily Website Visit", main = "20 Day Website Visit Forecast ")
lines(seq(481,500,1),f[[1]], col = "red")


# ASE
ASE=mean((f$f-df$Page.Loads[481:500])^2)
ASE #934133.1



#--------------- Short term prediction - 20 points ahead ---------------
f=fore.aruma.wge(df$Page,phi=c(-0.005399671 ,-0.654709018,  0.158526224),theta=c(-0.4246388 ,-0.9999976),s=7, n.ahead=20,limits=T, lastn=F, plot=T)
plot(as.numeric(df$Page), type = "l", xlim = c(1,520),ylim=c(-5000,10000))
lines(seq(500,519,1),f[[1]], col = "red")


#--------------- Long term prediction - 200 points ahead ---------------
f=fore.aruma.wge(df$Page,phi=c(-0.005399671 ,-0.654709018,  0.158526224),theta=c(-0.4246388 ,-0.9999976),s=7, n.ahead=200,limits=T, lastn=F, plot=T)
plot(as.numeric(df$Page), type = "l", xlim = c(1,710),ylim=c(-90000,80000))
lines(seq(500,699,1),f[[1]], col = "red")
```
==============================================================================================================
#=========================================== Multivariate Model ==============================================
==============================================================================================================

# Data import and clean
```{r}
library(dplyr)
library(tswge)
library(ggplot2)
library(GGally)
library(tseries)
library(vars)

df=read.csv("~/Desktop/SMU/DS 6373 Time Series/Project/daily-website-visitors.csv")
dim(df) #2167 entries and 5 variables, Page.Loads is the response variable. 

df=df[1:500,] #Trim down the data



#--------------- Data cleaning - checking NA and data type---------------
sum(is.na(df$col)) # No NA values

#--------------- Data overview---------------
plotts.sample.wge(df$Page.Loads) 
mean(df$Page.Loads)
```

#============================= Model 4 - MLR with correlated errors model - (Multivariate model) ============================
```{r}
# Checking cross correlation relationship => No lag relationship required
ccf(df$Page.Loads,df$Unique.Visits)
ccf(df$Page.Loads,df$First.Time.Visits)
ccf(df$Page.Loads,df$Returning.Visits)
colnames(df)[1]="Day"
str(df)


fit=lm(df$Page.Loads~df$Day+df$Unique.Visits+df$First.Time.Visits+df$Returning.Visits)
aic.wge(fit$residuals,p=0:14, q=0:0)

est=arima(df$Page.Loads,order=c(7,0,0),xreg=cbind(df$Day,df$Unique.Visits,df$First.Time.Visits,df$Returning.Visits))
est   # Significant terms :Day, Unique.Visits, First.Time.Visits, Returning.Visits 

# MLR regression equation : 163.4299-0.4576*(Day)+2.5905*(Unique.Visits)-1.3678*(First.Time.Visits)-0.3087*(Returning.Visits)


acf(est$residuals) # Visually looks white noise 
ljung.wge(est$residuals,K=24)
ljung.wge(est$residuals,K=48) # Both Ljung-Box method FTR null hypothesis -> MLR model seems a good fit. 

Data <- subset(df, select = -Page.Loads )
Data
predsMLR=predict(est,newxreg=Data[481:500,])
predsMLR

#--------------- Validating the model - Last 20 data points - ASE -----------------


plot(as.numeric(df$Page.Loads), type = "l", xlim = c(1,510),ylab = "Daily Website Visit", main = "20 Day Website Visit Forecast ")
lines(seq(481,500,1),preds$pred, col = "red")

# ASE
ASE=mean((predsMLR$pred-df$Page.Loads[481:500])^2)
ASE  # 10402.91



#===================== Short term Horizon prediction using forecasted regressors - 20 days ahead=====================

#forecast Unique.Visits
plotts.sample.wge(df$Unique.Visits) #freq near .0192 (annual)
df_U7 = artrans.wge(df$Unique.Visits, phi.tr=c(rep(0,6),1))

plotts.sample.wge(df_U7)
aic5.wge(df_U7) #picks ARMA(3,2) assume stationary
aic5.wge(df_U7,type = "bic") #picks ARMA(3,2) 
ljung.wge(df_U7)$pval
ljung.wge(df_U7, K = 48)$pval 
fit=est.arma.wge(df_U7,p=1,q=2)
predsU = fore.aruma.wge(df$Unique.Visits,phi=c(0.8344297),theta=c(-0.161865,0.1314683),s=7,n.ahead = 20,lastn=FALSE,plot=TRUE, limits=FALSE)
plot(predsU$f, type = "l")
plot(seq(1,500,1), df$Unique.Visits, type = "l",xlim = c(0,530), ylab = "Visit count", main = "20 Day Unique.Visit Forecast")
lines(seq(500,519,1), predsU$f, type = "l", col = "red")


### Forecast First.Time.Visits ###
plotts.sample.wge(df$First.Time.Visits) 
df_F7 = artrans.wge(df$First.Time.Visits, phi.tr=c(rep(0,6),1))

plotts.sample.wge(df_F7)
aic5.wge(df_F7) #picks ARMA(3,2) assume stationary
aic5.wge(df_F7,type = "bic") #picks ARMA(3,2) 
ljung.wge(df_F7)$pval
ljung.wge(df_F7, K = 48)$pval 
fit=est.arma.wge(df_F7,p=1,q=2)
predsF = fore.aruma.wge(df$First.Time.Visits,phi=c(0.8287913),theta=c(-0.1436662, 0.1232416),s=7,n.ahead = 20)
plot(predsF$f, type = "l")
plot(seq(1,500,1), df$Unique.Visits, type = "l",xlim = c(0,530), ylab = "Visit count", main = "20 Day First.Time.Visit Forecast")
lines(seq(500,519,1), predsF$f, type = "l", col = "red")

### Forecast Returning.Visits ###
plotts.sample.wge(df$Returning.Visits) 
df_R7 = artrans.wge(df$Returning.Visits, phi.tr=c(rep(0,6),1))

plotts.sample.wge(df_F7)
aic5.wge(df_R7) #picks ARMA(1,0) 
aic5.wge(df_R7,type = "bic") #picks ARMA(1,0) 
ljung.wge(df_R7)$pval
ljung.wge(df_R7, K = 48)$pval 
fit=est.arma.wge(df_R7,p=1,q=0)
predsR = fore.aruma.wge(df$First.Time.Visits,phi=c(0.6954018),s=7,n.ahead = 20)
plot(predsR$f, type = "l")
plot(seq(1,500,1), df$Unique.Visits, type = "l",xlim = c(0,530), ylab = "Visit count", main = "20 Day Returning.Visit Forecast")
lines(seq(500,519,1), predsR$f, type = "l", col = "red")

ksfit = lm(Page.Loads~Unique.Visits+First.Time.Visits+Returning.Visits+Day, data = df)
plotts.sample.wge(ksfit$residuals)
phi = aic.wge(ksfit$residuals) #ARMA(4,1)

fit = arima(df$Page.Loads,order = c(phi$p,0,phi$q), seasonal = list(order = c(0,1,0), period = 7), xreg = cbind(df$Unique.Visits, df$First.Time.Visits, df$Returning.Visits,df$Day))


#Forecasting Page.Loads for the next 20days 
next20 = data.frame(Unique = predsU$f, First = predsF$f, Return = predsR$f, Day = seq(500,519,1))
#get predictions
predsP = predict(fit,newxreg = next20)
#plot next 20 cmort wrt time
plot(seq(1,500,1), df$Page.Loads, type = "l",xlim = c(0,528), ylab = "Visit count", main = "20 Day Daily Website Forecast")
lines(seq(500,519,1), predsP$pred, type = "l", col = "red")



#===================== Long term Horizon prediction - using forecasted regressors - 200 points ahead =================

predsU = fore.aruma.wge(df$Unique.Visits,phi=c(0.8344297),theta=c(-0.161865,0.1314683),s=7,n.ahead = 200)
predsF = fore.aruma.wge(df$First.Time.Visits,phi=c(0.8287913),theta=c(-0.1436662, 0.1232416),s=7,n.ahead = 200)
predsR = fore.aruma.wge(df$First.Time.Visits,phi=c(0.6954018),s=7,n.ahead = 200)

# Forecasting Page.Loads for the next 200 days
next200 = data.frame(Unique = predsU$f, First = predsF$f, Return = predsR$f, Day = seq(500,699,1))
#get predictions
predsP = predict(fit,newxreg = next200)
#plot next 20 cmort wrt time
plot(seq(1,500,1), df$Page.Loads, type = "l",xlim = c(0,730), ylab = "Visit count", main = "200 Day Daily Website Forecast")
lines(seq(500,699,1), predsP$pred, type = "l", col = "red")

```

#========================================== Model 5 - VAR - (Multivariate model) ==========================================
```{r}
# Checking cross correlation relationship => No lag relationship required
ccf(df$Page.Loads,df$Unique.Visits)
ccf(df$Page.Loads,df$First.Time.Visits)
ccf(df$Page.Loads,df$Returning.Visits)
colnames(df)[1]="Day"

#VAR Model 

VARselect(cbind(df$Page.Loads, df$Day, df$Unique.Visits, df$First.Time.Visits, df$Returning.Visits),lag.max = 10, type = "const")
# VARselect(cbind(df$Page.Loads, df$Unique.Visits, df$First.Time.Visits, df$Returning.Visits),lag.max = 10, type = "both")

#VAR with p = 1 since no lag relationship among variables
PageVAR = VAR(cbind(df$Page.Loads[1:500], df$Day[1:500], df$Unique.Visits[1:500], df$First.Time.Visits[1:500], df$Returning.Visits[1:500]), type = "const")
preds=predict(PageVAR,n.ahead=20)

#Plot
plot(seq(1,500,1), df$Page.Loads, type = "l",xlim = c(0,520), ylab = "Daily Website Visit", main = "20 Day Website Visit Forecast ")
lines(seq(481,500,1), preds$fcst$y1[,1], type = "l", col = "red")

# Fanchart
fanchart(preds,plot.type = "multiple", colors="red")

# ASE
ASE = mean((df$Page.Loads[481:500] - preds$fcst$y1[,1])^2)
ASE
```


#======================== Model 6 - Neural Network model using KNOWN variables - (Multivariate model) ========================
```{r}
library(nnfor)
set.seed(2)

#------------ MLP Using KNOWN three variable (Unique.Visits, First.Time.Visits, and Returning.Visits) ------------
colnames(df)[1]="Day"
DFsmall = df[1:480,]

# ITsmallDF = data.frame(Unique.Visits=ts(DFsmall$Unique.Visits),First.Time.Visits=ts(DFsmall$First.Time.Visits),Returning.Visits=ts(DFsmall$Returning.Visits))
ITsmallDF = data.frame(Day=ts(DFsmall$Day),Unique.Visits=ts(DFsmall$Unique.Visits),First.Time.Visits=ts(DFsmall$First.Time.Visits),Returning.Visits=ts(DFsmall$Returning.Visits))

fit.mlp = mlp(ts(DFsmall$Page.Loads),reps = 30,comb = "mean",xreg = ITsmallDF)
fit.mlp
plot(fit.mlp)

SMDF = data.frame(Day=ts(df$Day),Unique.Visits=ts(df$Unique.Visits),First.Time.Visits=ts(df$First.Time.Visits),Returning.Visits=ts(df$Returning.Visits))
fore.mlp = forecast(fit.mlp, h = 20, xreg = SMDF)
plot(fore.mlp)

plot(df$Page.Loads, type = "l", ylab = "Daily website visits", main = "20 day Daily Website Visit Forecast")
lines(seq(481,500,1),fore.mlp$mean,col = "red")

ASE = mean((df$Page.Loads[481:500] - fore.mlp$mean)^2)
ASE   # 63188.18
```


#==================== Model 7 - Neural Network model using Forecasted variables - (Multivariate model) ========================
```{r}
#---------- Using forecast of three variables (Unique.Visits, First.Time.Visits, and Returning.Visits) -----------

# Unique.Visits
fit.mlp.unique = mlp(ts(DFsmall$Unique.Visits),reps = 30, comb = "mean")
plot(fit.mlp.unique)
fore.mlp.unique = forecast(fit.mlp.unique, h = 20)
plot(fore.mlp.unique)

# First.Time.Visits
fit.mlp.first = mlp(ts(DFsmall$First.Time.Visits),reps = 30, comb = "mean")
plot(fit.mlp.first)
fore.mlp.first = forecast(fit.mlp.first, h = 20)
plot(fore.mlp.first)

# Returning.Visits
fit.mlp.return = mlp(ts(DFsmall$Returning.Visits),reps = 30, comb = "mean")
plot(fit.mlp.return)
fore.mlp.return = forecast(fit.mlp.return, h = 20)
plot(fore.mlp.return)

#package them up in data frame.
CMDF_fore = data.frame(Day = ts(seq(1,500,1)),Unique = ts(c(DFsmall$Unique.Visits,fore.mlp.unique$mean)), First = ts(c(DFsmall$First.Time.Visits,fore.mlp.first$mean)),Return=ts(c(DFsmall$Returning.Visits,fore.mlp.return$mean)))
CMDF_fore

#forecast cmort using mlp with forecasted xreg
ITsmallDF = data.frame(Day = ts(DFsmall$Day),Unique = ts(DFsmall$Unique.Visits), First = ts(DFsmall$First.Time.Visits),Return = ts(DFsmall$Returning.Visits))
fit.mlp = mlp(ts(DFsmall$Page.Loads),reps = 30,comb = "mean",xreg = ITsmallDF)
fit.mlp
plot(fit.mlp)

fore.mlp = forecast(fit.mlp, h = 20, xreg = CMDF_fore)
plot(fore.mlp)
ASE = mean((df$Page.Loads[481:500] - fore.mlp$mean)^2)
ASE  #399740.1

#Plot
plot(seq(1,500,1), df$Page.Loads, type = "l",xlim = c(0,520), ylab = "Daily Website Visit", main = "20 Day Website Visit Forecast Forecast")
lines(seq(481,500,1), fore.mlp$mean, type = "l", col = "red")


#=====================  Short term Horizon Forecasting using Forecasted regressors =====================
library(nnfor)
# Unique.Visits
fit.mlp.unique = mlp(ts(df$Unique.Visits),reps = 30, comb = "mean")
plot(fit.mlp.unique)
fore.mlp.unique = forecast(fit.mlp.unique, h = 20)
plot(fore.mlp.unique)

# First.Time.Visits
fit.mlp.first = mlp(ts(df$First.Time.Visits),reps = 30, comb = "mean")
plot(fit.mlp.first)
fore.mlp.first = forecast(fit.mlp.first, h = 20)
plot(fore.mlp.first)


# Returning.Visits
fit.mlp.return = mlp(ts(df$Returning.Visits),reps = 30, comb = "mean")
plot(fit.mlp.return)
fore.mlp.return = forecast(fit.mlp.return, h = 20)
plot(fore.mlp.return)

#package them up in data frame.

CMDF_fore = data.frame(Day = ts(seq(1,520,1)),Unique = ts(c(df$Unique.Visits,fore.mlp.unique$mean)), First = ts(c(df$First.Time.Visits,fore.mlp.first$mean)),Return=ts(c(df$Returning.Visits,fore.mlp.return$mean)))
CMDF_fore

#forecast Page.Loads using mlp with forecasted xreg
ITDF = data.frame(Day = ts(df$Day),Unique = ts(df$Unique.Visits), First = ts(df$First.Time.Visits),Return = ts(df$Returning.Visits))
fit.mlp = mlp(ts(df$Page.Loads),reps = 30,comb = "mean",xreg = ITDF)
fit.mlp
plot(fit.mlp)

fore.mlp = forecast(fit.mlp, h = 20, xreg = CMDF_fore)
plot(fore.mlp)


#Plot
plot(seq(1,500,1), df$Page.Loads, type = "l",xlim = c(0,540), ylab = "Daily Website Visit", main = "20 Day Website Visit Forecast Forecast")
lines(seq(500,519,1), fore.mlp$mean, type = "l", col = "red")


#=================== Long term Horizon Forecasting using Forecasted regressors ================

# Unique.Visits
fit.mlp.unique = mlp(ts(df$Unique.Visits),reps = 30, comb = "mean")
plot(fit.mlp.unique)
fore.mlp.unique = forecast(fit.mlp.unique, h = 200)
plot(fore.mlp.unique)

# First.Time.Visits
fit.mlp.first = mlp(ts(df$First.Time.Visits),reps = 30, comb = "mean")
plot(fit.mlp.first)
fore.mlp.first = forecast(fit.mlp.first, h = 200)
plot(fore.mlp.first)


# Returning.Visits
fit.mlp.return = mlp(ts(df$Returning.Visits),reps = 30, comb = "mean")
plot(fit.mlp.return)
fore.mlp.return = forecast(fit.mlp.return, h = 200)
plot(fore.mlp.return)


#package them up in data frame.
CMDF_fore = data.frame(Day = ts(seq(1,700,1)),Unique = ts(c(df$Unique.Visits,fore.mlp.unique$mean)), First = ts(c(df$First.Time.Visits,fore.mlp.first$mean)),Return=ts(c(df$Returning.Visits,fore.mlp.return$mean)))
CMDF_fore


#forecast Page Loads using mlp with forecasted xreg
ITDF = data.frame(Day = ts(df$Day),Unique = ts(df$Unique.Visits), First = ts(df$First.Time.Visits),Return = ts(df$Returning.Visits))
fit.mlp = mlp(ts(df$Page.Loads),reps = 30,comb = "mean",xreg = ITDF)
fit.mlp
plot(fit.mlp)


fore.mlp = forecast(fit.mlp, h = 200, xreg = CMDF_fore)
plot(fore.mlp)


#Plot
plot(seq(1,500,1), df$Page.Loads, type = "l",xlim = c(0,720), ylab = "Daily Website Visit", main = "200 Day Website Visit Forecast Forecast")
lines(seq(500,699,1), fore.mlp$mean, type = "l", col = "red")
```

#===================== Model 8 - Ensemble model - (MLR + Neural network with known variables) =====================
```{r}
ensemble  = (as.numeric(predsMLR$pred) + as.numeric(fore.mlp$mean))/2

#Plot
plot(seq(1,500,1), df$Page.Loads, type = "l",xlim = c(0,520), ylab = "Daily Website Visit", main = "20 Day Website Visit Forecast Forecast")
lines(seq(481,500,1), ensemble, type = "l", col = "red")

ASE = mean((df$Page.Loads[481:500] - ensemble)^2)
ASE 
```